---
title: "R Session - mldr.datasets Package"
output:
  html_document:
    df_print: paged
---

This notebook shows how to use the `mldr.datasets` package to retrieve multi-label datasets from the [Cometa](https://cometa.ujaen.es) repository, partition these datasets and writing them using disparate file formats. You can run the code by yourself by loading this file from RStudio.

## Installing and loading the package

`mldr.datasets` is available at CRAN, so you can install as any other R package through the `install.packages()` function. Development version is available in GitHub.

```{r warning=FALSE}
# install.packages("mldr.datasets"           # Uncomment this line if you need to install the package from CRAN
# remotes::install_github("fcharte/mldr.datasets")    # Uncomment this line if you want to install the latest version (in development) from GitHub

library(mldr.datasets)

```

## Query the available datasets 

```{r}
available.mldrs()[c(1,16,20),] # Get some meta-data columns from three of the available datasets

available.mldrs()  # Simply call available.mldrs() to retrieve the updated full list from cometa.ujaen.es
```

## Download a dataset from the repository

```{r}
databib <- bibtex() # Load the bibtex dataset, downloading it if it is not locally available

summary(databib) # Get a summary of traits of the data

cat(toBibtex(emotions)) # Retrieves citation information of a previously loaded dataset: emotions
```

## Dataset partitioning and exporting to other file fomat

```{r}
# Divide the emotions dataset into 5 folds and write them using MULAN and CSV
# file formats, taking into account the sparsity level
write.mldr(random.kfolds(emotions, k = 5), format=c("MULAN", "CSV"), 
           sparse = sparsity(emotions) > 0.5, basename="emotions",
           noconfirm = TRUE)

```

