---
title: "R Session - mldr Package"
output:
  html_document:
    df_print: paged
---

This notebook shows how to use the `mldr` package to load multi-label datasets, perform exploratory data analisys tasks, etc. You can run the code by yourself by loading this file from RStudio.

## Installing and loading the package
```{r}

```

`mldr` is available at CRAN, so you can install as any other R package through the `install.packages()` function. Development version is available in GitHub.

```{r}
# install.packages("mldr")                   # Uncomment this line if you need to install the package from CRAN
# remotes::install_github("fcharte/mldr")    # Uncomment this line if you want to install the latest version (in development) from GitHub

library(mldr)
```

## Loading a multi-label dataset and exploring it

```{r}
emotions <- mldr("emotions")
summary(emotions)  # A summary of metrics
emotions$labels    # Details about the labels in emotions
emotions$labelsets # Details about the labelsets
```


## Obtaining citation info for the dataset
```{r}
emotions$bibtex
```


## Generate some plots from the dataset

```{r}
# Label concurrence plot
plot(genbase, type = "LC") # Plots all labels
plot(genbase) # Same as above
plot(genbase, title = "genbase dataset", color.function = heat.colors) # Changes the title and color
plot(genbase, labelCount = 10) # Randomly selects 10 labels to plot
plot(genbase, labelIndices = genbase$labels$index[1:10]) # Plots info of first 10 labels

# Label bar plot
plot(emotions, type = "LB", col = terrain.colors(emotions$measures$num.labels))

# Label histogram plot
plot(emotions, type = "LH")

# Cardinality histogram plot
plot(emotions, type = "CH")

# Attributes by type
plot(emotions, type = "AT", cex = 0.85)

# Labelset histogram
plot(emotions, type = "LSH")
```

## Obtain a label concurrence report

```{r}
concurrenceReport(emotions)  # Details about label concurrence
```

## Evaluate a set of artificial  predictions

```{r}
# Get the true labels in emotions
predictions <- as.matrix(emotions$dataset[, emotions$labels$index])
# and introduce some noise (alternatively get the predictions from some classifier)
noised_labels <- cbind(sample(1:593, 200, replace = TRUE), sample(1:6, 200, replace = TRUE))
predictions[noised_labels] <- sample(0:1, 100, replace = TRUE)
# then evaluate predictive performance
res <- mldr_evaluate(emotions, predictions)
str(res)
plot(res$roc, main = "ROC curve for emotions")
```

## Interactive user interface
```{r}
if (interactive()) {
  mldrGUI() # Call this function to open the interactive GUI of the mldr package
  help(package = "mldr") # Opens the index of help topics for mldr
  browseVignettes(package = "mldr") # Opens the vignettes with a broader description of the package
}
```

