---
title: "R Session - mlr Package"
output:
  html_document: default
---

This notebook shows how to use the `mlr` package to train two classifiers and evaluate them. You can run the code by yourself by loading this file from RStudio.

## Installing and loading the package

`mlr` is available at CRAN, so you can install as any other R package through the `install.packages()` function. Development version is available in GitHub.

```{r}
# install.packages("mlr")                   # Uncomment this line if you need to install the package from CRAN
# remotes::install_github("mlr-org/mlr")    # Uncomment this line if you want to install the latest version (in development) from GitHub

library(mlr)
```

## Prepare the data

```{r}
# To work with data in an mldr object we need to apply some  changes
mld <- mldr.datasets::flags
mldmlr <- data.frame( # Builds a data.frame changing the type of labels to logical
                 mld$dataset[,mld$attributesIndexes], 
                 sapply(mld$dataset[,mld$labels$index], as.logical))
                 
mldmlr[sapply(mldmlr, is.character)] <-  # Change "character" columns to "factor"
            lapply(mldmlr[sapply(mldmlr, is.character)], as.factor)
```


## Create the mlr task

```{r}
mldtask <- makeMultilabelTask(id = "MLLTest", 
                  data = mldmlr, target = row.names(mld$labels))

mldtask # Explore the mlr task object

```

## Train two classifiers

```{r}
# Test one adaptation-based algorithm and one transformation-based
class1 <- makeLearner("multilabel.randomForestSRC")
class2 <- makeMultilabelBinaryRelevanceWrapper(
              makeLearner("classif.rpart", predict.type = "prob"))
model1 <- train(class1, mldtask, subset = 1:150)
model2 <- train(class2, mldtask, subset = 1:150)

```

## Test and evaluate the classifiers

```{r}
predict1 <- predict(model1, task = mldtask, subset = 151:194)
predict2 <- predict(model2, task = mldtask, subset = 151:194)

measures <- list(multilabel.hamloss, multilabel.f1, multilabel.acc, multilabel.subset01)

performance(predict1, measures = measures)
performance(predict2, measures = measures)

```

